Analysis for Project

### 2021-03-26 analysis/analysis.Rmd
use ordered factor for parent's highest degree

```{r}
#try a model
model1 <- glm(below_exp_grade~race+as.factor(year), data=acs, family=binomial)
model2 <- update(model1, .~.+degree_mother+degree_father)
model3 <- update(model2, .~.+sqrt(family_income/10000)+own_home+parents_married)
model4 <- update(model3, .~.+foreign_born_mother+foreign_born_father)

@@

```{r}
resources_race <- acs %>% 
  group_by(race) %>%
  summarize(mean_age=mean(age),
            prop_foreign_born=mean(foreign_born),
            mean_fam_inc=mean(family_income),
            prop_own_home=mean(own_home),
            prop_parents_married=mean(parents_married),
            mean_age_parents=mean((age_birth_mother+age_birth_father)/2),
            prop_parent_foreign_born=mean(foreign_born_father | foreign_born_mother)) %>%
  ungroup() %>%
  filter(!str_detect(race,"Multiracial"))

>>>>

```{r}
#try a model
model1 <- glm(below_exp_grade~race+as.factor(year)+foreign_born, data=acs, family=binomial)
model2 <- update(model1, .~.+degree_mother+degree_father)
model3 <- update(model2, .~.+sqrt(family_income/10000)+own_home+parents_married)
model4 <- update(model3, .~.+foreign_born_mother+foreign_born_father)

@@

```{r}
resources_race <- acs %>% 
  group_by(race) %>%
  summarize(prop_held_back=mean(below_exp_grade),
            mean_age=mean(age),
            prop_foreign_born=mean(foreign_born),
            mean_fam_inc=mean(family_income),
            prop_own_home=mean(own_home),
            prop_hs_diploma=mean(degree_father>="HS diploma" | 
                                   degree_mother>="HS diploma"),
            prop_ba_degree=mean(degree_father>="BA degree" | 
                                  degree_mother>="BA degree"),
            prop_parents_married=mean(parents_married),
            mean_age_parents=mean((age_birth_mother+age_birth_father)/2),
            prop_parent_foreign_born=mean(foreign_born_father | 
                                            foreign_born_mother)) %>%
  ungroup() %>%
  filter(!str_detect(race,"Multiracial"))
